Do we need detailed demographic data to forecast plant population responses to climate change?

### 2016-05-15 manuscript/manuscript.Rmd
adds dataset description table; adds discussion paragraph on horizons

@@

Tables
------

>>>>

We also expected IPM forecast accuracy to decline at a lower rate than the QBM as the forecast horizon increased.
Indeed, many have argued that more mechanistic models produce better predictions, especially under novel conditions [@Evans2012b; @Schindler2015b].
Likewise, the IPM explicitly models the processes of recruitment and survival that may be poorly represented in the QBM since recruitment and survival mainly affect small plants that contribute little to overall changes in percent cover.
But the addition and subtraction of small plants can have large effects on population growth over time and potentially lead to a longer forecast horizon for models that better represent the plant life cycle.
We found no evidence for a difference between the IPM and QBM forecast horizons (Fig. 4).
Similar forecast horizons should be expected if both models adequately capture density-dependence and environmental forcing is negligble, as is the case for our models (Fig. 2).
In fact, only the forecast horizons for *P. secunda* noticeably differ (Fig. 4), and that is also the only species where we found the IPM to outperform the QBM when we included climate effects.

@@

Tables
------
\begin{table}[ht]
\centering
\caption{Description of data.} 
\begin{tabular}{llrr}
  \hline
Species & Vital Rate Model & Num. Obs. & Num. Quadrats\\ 
  \hline
  \emph{B. gracilis} & Growth & 5670 & 29 \\ 
       & Survival & 10102 & 33 \\ 
       & Recruitment & 304 & 33 \\ 
       & Percent cover & 281 & 29 \\ 
  \rule{0pt}{3ex} \emph{H. comata} & Growth & 1990 & 16 \\ 
       & Survival & 3257 & 18 \\ 
       & Recruitment & 304 & 18 \\ 
       & Percent cover & 171 & 17 \\ 
  \rule{0pt}{3ex} \emph{P. smithii} & Growth & 8052 & 19 \\ 
       & Survival & 11344 & 19 \\ 
       & Recruitment & 304 & 19 \\ 
       & Percent cover & 217 & 19 \\ 
  \rule{0pt}{3ex} \emph{P. secunda} & Growth & 3018 & 18 \\ 
       & Survival & 4650 & 18 \\ 
       & Recruitment & 304 & 18 \\ 
       & Percent cover & 197 & 18 \\ 
   \hline
\end{tabular}
\end{table}
